\begin{answer}
  All 8 cases of proposed kernels $K$ are trivially symmetric because
  $K_1, K_2, K_3$ are symmetric; and because the product of 2 real
  numbers is commutative (for (1f)).  Thanks to Mercer's theorem, it
  is sufficient to prove the corresponding properties for positive
  semidefinite matrices.  To differentiate between matrix and kernel
  function, we'll use $G_i$ to denote a kernel matrix (Gram matrix)
  corresponding to a kernel function $K_i$.

  \begin{enumerate}

  \item Kernel.  The sum of 2 positive semidefinite matrices is a
    positive semidefinite matrix: $\forall z\; z^T G_1 z \geq 0, z^T
    G_2 z \geq 0$ since $K_1, K_2$ are kernels.  This implies $\forall
    z\; z^T G z = z^T G_1 z + z^T G_2 z \geq 0$.

  \item Not a kernel.  Counterexample: Let $K_1$ be a kernel with positive definite matrix $G_1$ and let $K_2 = 2K_1$ (we are using
    (1c) here to claim $K_2$ is a kernel).  Then we have $\forall z\;
    z^T G z = z^T (G_1 - 2G_1) z = -z^T G_1 z < 0$.

  \item Kernel.  $\forall z\; z^T G_1 z \geq 0$, which implies
    $\forall z\; a z^T G_1 z \geq 0$.

  \item Not a kernel.  Counterexample: Let $K_1$ be a kernel with positive definite matrix $G_1$ and set $a = 1$.  Then we have $\forall
    z\; -z^T G_1 z \leq 0$.

  \item Kernel.  $K_1$ is a kernel, thus $\exists \phi^{(1)}$ such that
    $K_1(x, z) = \phi^{(1)} (x)^T \phi^{(1)} (z) = \sum_i \phi_i^{(1)} (x)
    \phi_i^{(1)} (z)$.  Similarly, $K_2$ is a kernel, thus $\exists
    \phi^{(2)}\; K_2(x, z) = \phi^{(2)} (x)^T \phi^{(2)} (z) = \sum_j
    \phi_j^{(2)} (x) \phi_j^{(2)} (z)$.
    \begin{align}
      K(x, z)
      &= K_1(x, z)K_2(x, z) \\
      &= \sum_i \phi_i^{(1)} (x) \phi_i^{(1)} (z) \sum_i \phi_i^{(2)}
      (x) \phi_i^{(2)} (z) \\
      &= \sum_i \sum_j \phi_i^{(1)} (x) \phi_i^{(1)} (z) \phi_j^{(2)}
      (x) \phi_j^{(2)} (z) \\
      &= \sum_i \sum_j (\phi_i^{(1)} (x) \phi_j^{(2)} (x))
      (\phi_i^{(1)} (z) \phi_j^{(2)} (z)) \\
      &= \sum_{(i,j)} \psi_{i, j}(x) \psi_{i, j}(z)
    \end{align}
    Where the last equality holds because that's how we define
    $\psi$.  We see $K$ can be written in the form $K(x, z) =
    \psi(x)^T \psi(z)$ so it is a kernel.

%    Here is an alternate super-slick linear-algebraic proof.  If $G$ is
%    the Gram matrix for the product $K_1 \times K_2$, then $G$ is a
%    principal submatrix of the Kronecker product $G_1 \otimes G_2$, where
%    $G_i$ is the Gram matrix for $K_i$. As the Kronecker product is
%    positive semi-definite, so are its principal submatrices.

  \item Kernel. Just let $\phi(x) = f(x)$, and since $f(x)$ is a
    scalar, we have $K(x, z) = \phi(x)^T \phi(z)$ and we are done.

  \item Kernel. Since $K_3$ is a kernel, the matrix $G_3$ obtained
    for \emph{any} finite set $\{x^{(1)},\ldots,x^{(\nexp)}\}$ is positive
    semidefinite, and so it is also positive semidefinite for the sets
    $\{\phi(x^{(1)}),\ldots,\phi(x^{(\nexp)})\}$.

  \item Kernel. By combining (1a) sum, (1c) scalar product, (1e)
    powers, (1f) constant term, we see that any polynomial of a kernel
    $K_1$ will again be a kernel.

  \end{enumerate}

\end{answer}
